---
output: github_document
always_allow_html: yes
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
asciicast::init_knitr_engine()
options(asciicast_knitr_svg = TRUE)
```
# asciicast

> Turn R scripts into terminal screencasts

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/asciicast)](https://cran.r-project.org/package=asciicast)
<!-- badges: end -->

asciicast takes an R script and turns it into an
[asciinema](https://asciinema.org/) cast. It can simulate typing, and
records all terminal output in real time as it happens.

## Features

* Input is an R script, output is a
  [v2 asciicast recording](https://github.com/asciinema/asciinema/blob/develop/doc/asciicast-v2.md).
* Record all terminal output in real time, as it happens.
* Simulate typing in the commands, with a configurable, randomized speed.
* Alternatively, whole comment blocks or expressions can just appear on
  the screen.
* Convert casts to SVG images using
  [svg-term](https://github.com/marionebl/svg-term). The package comes with
  its own svg-term bundle, no external dependencies are needed.
* Render a single frame of a cast as an SVG image.
* Configurable delay at the beginning, at the end and between paragraphs.
* [HTML widget](http://www.htmlwidgets.org), to be used in Rmarkdown
  documents, e.g. in vignettes.
* Read casts from asciinema JSON files (version 2), or from
  <https://asciinema.org> directly.
* Special knitr engine to create R markdown files with ascii casts. See
  the `asciicast-demo` vignette.
* Create ascii casts in GitHub READMEs via animated SVG files. See an
  example in `inst/examples` or the `README.Rmd` source of the README
  file you are reading.

## Limitations

* asciicast does not work in Windows yet, because of a the lack of a
  pseudo terminal. Maybe you can try running it on Linux in Docker?
* Recordings are currently real time, so if you "type in" a lot of
  code/text, that might take a while to record.
* Only syntactically correct R script files can be recorded.
* asciicast redefines `option("error")` currently, so if you want to
  set this option in your demo, that won't work.

## Installation

You can install the released version of asciicast from
[CRAN](https://CRAN.R-project.org):

``` r
install.packages("asciicast")
```

## Examples

See the [`inst/examples` directory](https://github.com/gaborcsardi/asciicast/tree/master/inst/examples)
for these examples.

### Hello world

The input script:

```{r echo = FALSE, results = "asis"}
cat("```\n")
cat(readLines("inst/examples/hello.R"), sep = "\n")
cat("```\n")
```

```{asciicast, file = "inst/examples/hello.R", cache = TRUE}
```

### Asciicast demo in asciicast

Input script that uses asciicast itself:

```{r echo = FALSE, results = "asis"}
cat("```\n")
cat(readLines("inst/examples/asciicast.R"), sep = "\n")
cat("```\n")
```

```{asciicast, file = "inst/examples/asciicast.R", cache = TRUE}
```

### Errors are recorded

Input script with errors:

```{r echo = FALSE, results = "asis"}
cat("```\n")
cat(readLines("inst/examples/errors.R"), sep = "\n")
cat("```\n")
```

```{asciicast, file = "inst/examples/errors.R", cache = TRUE}
```

## Related tools

* asciinema: https://asciinema.org/
* The original terminal session recorder:
  https://github.com/asciinema/asciinema
* svg-term: https://github.com/marionebl/svg-term,
  https://github.com/marionebl/svg-term-cli

## License

MIT @ [RStudio](https://github.com/rstudio)
