---
title: "asciicast example vignette"
author: "Gábor Csárdi"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{asciicast example vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Example

This is an example vignette for creating asciinema screen casts.
To include a screencast in your document, you need to do two steps.
The first is to initialize the asciicast engine:

````
```{r echo = FALSE, results = "hide"}`r ''`
asciicast::init_knitr_engine()
```
````

```{r echo = FALSE, results = "hide"}
asciicast::init_knitr_engine()
```

After this, for the chunks that you want to display in an asciinema
player, use the asciicast engine:

````
```{asciicast}`r ''`
# This will be an ascii cast
# Let's evaluate some code
head(mtcars)
```
````

This will produce the following cast:

```{asciicast cache = TRUE}
# This will be an ascii cast
# Let's evaluate some code
head(mtcars)
```

## Changing parameters

You can include a DCF header in the asciicast, to set some parameters, e.g.
the height of the widget.

````
```{asciicast}`r ''`
#' Rows: 10

# No much here, so avoid a big widget
1 + 2 + 3 + 4
```
````

```{asciicast cache = TRUE}
#' Rows: 5

# Not much here, so avoid a big widget
1 + 2 + 3 + 4
```

## Caching

Recording the asciinema casts might take long, as everything happens
in real time. You can tell knitr to cache the results, as long as the
code of the chunk is unchanged. E.g. the previous chunk with caching
looks like this:

````
```{asciicast cache = TRUE}`r ''`
#' Rows: 5

# Not much here, so avoid a big widget
1 + 2 + 3 + 4
```
````

## Casting a script from a file

It is possible to read the R code of a cast from a file, instead of
specifying it in the code chunk. The advantage of this is that it is easier
to use the code in the R scripts for other purposes.

````
```{asciicast file = "../inst/examples/hello.R"}`r ''`
```
````

```{asciicast file = "../inst/examples/hello.R", cache = TRUE}
```

Unfortunately caching does not work well for external files, the knitr
cache does not know that it needs to re-record a chunk when the file
changes.

See the documentation for the other parameters that you can set in the
header. Enjoy!
