---
title: "asciicast example vignette"
author: "Gábor Csárdi"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{asciicast example vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This is an example vignette for creating asciinema ascii screen casts.
To include a screencast in your document, you need to do two steps.
The first is to initialize the asciicast engine:

````
```{r echo = FALSE, results = "hide"}`r ''`
asciicast::init_knitr_engine()
```
````

```{r echo = FALSE, results = "hide"}
asciicast::init_knitr_engine()
```

After this, for the chunks that you want to display as an ascii cast,
use the asciicast engine:

````
```{asciicast}`r ''`
# This will be an ascii cast
# Let's evaluate some code
head(mtcars)
```
````

This will produce the following cast:

```{asciicast}
# This will be an ascii cast
# Let's evaluate some code
head(mtcars)
```

You can include a DCF header in the asciicast, to set some parameters, e.g.
the height of the widget.

````
```{asciicast}`r ''`
#' Height: 10

# No much here, so avoid a big widget
1 + 2 + 3 + 4
```
````

```{asciicast}
#' Height: 5

# Not much here, so avoid a big widget
1 + 2 + 3 + 4
```

See the documentation for the other parameters that you can set in the
header. Enjoy!
